### 2020-06-24 include/clust_summ.tex
Cleaned gitignore, analyses with seosaw v2.6

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mon, Dec 16, 2019 - 11:33:55
\begin{table}[!htbp] \centering 
  \caption{} 
  \label{clust_summ} 
\begin{tabular}{@{\extracolsep{5pt}} ccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
clust4 & c\_dom & c\_ind & n\_plots & n\_species\_raref & stems\_ha & agb\_ha \\ 
\hline \\[-1.8ex] 
1 & Julbernadia spp., Brachystegia spiciformis, Baikeaea plurijuga & Diplorhynchus condylocarpon, Burkea africana, Pseudolachnostylis maprouneifolia & 687 & 11(11.2) & 170(145.3) & 37(34.68) \\ 
2 & Julbernadia spp., Brachystegia spp., Isoberlinia angolensis & Julbernardia paniculata, Isoberlinia angolensis, Brachystegia longifolia & 757 & 18(17.6) & 215(171.7) & 48.8(43.7) \\ 
3 & Spirostachys africana, Senegalia spp., Euclea racemosa & Baikiaea plurijuga, Senegalia ataxacantha, Combretum collinum & 226 & 10(10) & 165(157.5) & 46(47.81) \\ 
4 & Colophospermum mopane & Colophospermum mopane, Combretum spp. & 99 & 7(8.2) & 190(155.7) & 41.5(36.93) \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

>>>>

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Wed, Jun 24, 2020 - 12:22:31
\begin{table}[!htbp] \centering 
  \caption{} 
  \label{clust_summ} 
\begin{tabular}{@{\extracolsep{5pt}} ccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
clust4 & c\_dom & c\_ind & n\_plots & n\_species\_raref & stems\_ha & agb\_ha \\ 
\hline \\[-1.8ex] 
Acacia shrubland & Baikiaea plurijuga, Burkea africana, Pterocarpus angolensis & Burkea africana, Baikiaea plurijuga, Pterocarpus angolensis & 188 & 12(10.3) & 181(166.5) & 54.5(61.33) \\ 
Core miombo & Brachystegia spiciformis, Julbernardia paniculata, Brachystegia boehmii & Parinari curatellifolia, Uapaca kirkiana, Brachystegia spiciformis & 523 & 20(16.9) & 204(142.5) & 44.2(36.11) \\ 
Marginal miombo & Spirostachys africana, Senegalia burkei, Senegalia nigrescens & Euclea racemosa, Vachellia nilotica, Spirostachys africana & 466 & 12(13.7) & 178(129.5) & 36.9(26.98) \\ 
Mopane & Colophospermum mopane, Androstachys johnsonii, Kirkia acuminata & Colophospermum mopane, Psuedolachnostylis maprouneifolia, Lannea discolor & 58 & 10(10.2) & 186(125.6) & 42.7(32.83) \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}
